Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-11-15 manuscript.tex
Add missing punctuation in equations
Explain Kronecker's delta

\begin{equation}
    V(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{1}{\ell}
        \kappa\  dr^\prime d\phi^\prime d\lambda^\prime,
    \label{eq:tesspot}
\end{equation}
\begin{equation}
    g_{\alpha}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{\Delta_\alpha}{\ell^3}
        \kappa\ dr^\prime d\phi^\prime d\lambda^\prime,
    \label{eq:tessgrav}
\end{equation}
\noindent
and
\begin{equation}
    g_{\alpha\beta}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        I_{\alpha\beta}
        \ \kappa\ dr^\prime d\phi^\prime d\lambda^\prime.
    \label{eq:tesstensor}
\end{equation}
\begin{equation}
    I_{\alpha\beta} =
    \left(
        \frac{3\Delta_{\alpha} \Delta_{\beta}}{\ell^5} -
        \frac{\delta_{\alpha\beta}}{\ell^3}
    \right)
    \label{eq:tesstensorkernel}
\end{equation}

\noindent
where $\alpha, \beta \in \{x, y, z\}$,
$\rho$ is the density,
$G = 6.674\times10^{-11}\ m^3kg^{-1}s^{-1}$ is the gravitational constant,
and

@@

\begin{equation}
    d = \left[
        r^2 + r_t^2 - 2 r r_t \cos\psi_t
        \right]^{\frac{1}{2}}.
    \label{eq:distance}
\end{equation}
\begin{equation}
    \cos\psi_t =
        \sin\phi\sin\phi_t + \cos\phi\cos\phi_t\cos(\lambda - \lambda_t)
\end{equation}

>>>>

\begin{equation}
    V(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{1}{\ell}
        \kappa\  dr^\prime d\phi^\prime d\lambda^\prime,
    \label{eq:tesspot}
\end{equation}
\begin{equation}
    g_{\alpha}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{\Delta_\alpha}{\ell^3}
        \kappa\ dr^\prime d\phi^\prime d\lambda^\prime,
    \label{eq:tessgrav}
\end{equation}
\noindent
and
\begin{equation}
    g_{\alpha\beta}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        I_{\alpha\beta}
        \ \kappa\ dr^\prime d\phi^\prime d\lambda^\prime ,
    \label{eq:tesstensor}
\end{equation}
\begin{equation}
    I_{\alpha\beta} =
    \left(
        \frac{3\Delta_{\alpha} \Delta_{\beta}}{\ell^5} -
        \frac{\delta_{\alpha\beta}}{\ell^3}
    \right) ,
    \label{eq:tesstensorkernel}
\end{equation}

\noindent
where $\alpha, \beta \in \{x, y, z\}$,
$\rho$ is the density,
$G = 6.674\times10^{-11}\ m^3kg^{-1}s^{-1}$ is the gravitational constant,
$\delta_{\alpha\beta}$ is Kronecker's delta
($\delta_{\alpha\beta} = 1$ if $\alpha = \beta$
and $\delta_{\alpha\beta} = 0$ if $\alpha \neq \beta$),
and

@@

\begin{equation}
    d = \left[
        r^2 + r_t^2 - 2 r r_t \cos\psi_t
        \right]^{\frac{1}{2}} ,
    \label{eq:distance}
\end{equation}
\begin{equation}
    \cos\psi_t =
        \sin\phi\sin\phi_t + \cos\phi\cos\phi_t\cos(\lambda - \lambda_t) .
\end{equation}
